---
title: "Categorical Data Analysis - PSET 2"
author: "Josemari Feliciano"
output:
  pdf_document: default
  html_notebook: default
---

#### Problem 1:  Calculate the likelihood for this data using a Poisson distribution with μ ranging from 0.5 to 10 and using 0.5 as the interval length.

Copies the data from homework page:

```{r}
lambda <- seq(0.5,10,0.5)
claims <- c(4,6,2,4,3,1,3,2,7,5)
```

Write a function that can calculate likelihood for me and will report info in a matrix:

```{r}
likelihood_calculator <- function(data,lambda_vector){
  likelihood_all <- c()
  for(l in lambda_vector){
    data2 <- exp(-l) * (l ^ data) / factorial(data)
    likelihood_all <- c(likelihood_all,prod(data2))
  }
  return(likelihood_all)
}

likelihood <- likelihood_calculator(claims,lambda)
results <- rbind(lambda,likelihood)
```

__SOLUTION TO QUESTION 1__ Above, I printed the necessary solution above with lambda and its corresponding likelihood.

__SOLUTION TO QUESTION 2__ Below, using claims number, MLE for u is 3.7.

```{r}
mean(claims)
```

__SOLUTION TO QUESTION 3__ Using calculations I did for question 1 and the code __BELOW__, MLE is: 3.5

```{r}
results[,which.max(likelihood)]
```
